---
title: "Citation Screening Comparison: Search Term Retrieval Comparison"
author: "Emma Wilson"
output: html_document
---

## Load packages

```{r, message=FALSE}
# Running RStudio and R Version 4.2.1

library(caret)   #V6.0-92
library(dplyr)   #V1.0.9
```

## Read in Data

Read in the dataset containing all cleaned and validated screening data, and the dataset containing titles from the restricted term search.

```{r}
# Dataset of all manual screening decisions and regex decisions
dat <- read.csv("data/screening_data_clean.csv", stringsAsFactors = T)

#Dataset containing titles of all records from restricted search terms
restrictedsearch <- read.csv("data-raw/restricted_search_20220505_titles.csv", stringsAsFactors = F)
```

## Match Data Using Title

```{r}
# Filter full dataset to identify records where title also appears in restricted terms search
matched <- dat %>%
  filter(Title %in% restrictedsearch$Title)
```

# Create New Column to Store Information

```{r}
# Create new column and assign variable 'Yes'
matched$InRestrictedSearch <- "Yes"

# Subset data not matching on title and create new column for 'No'
notmatched <- dat %>%
  filter(!Title %in% restrictedsearch$Title) %>%
  mutate(InRestrictedSearch = "No")

#Merge data back together
dat <- rbind(matched, notmatched)
```

# Identify If Any Included Studies Would Have Been Missed by Restricted Search

```{r}
# Find missed studies
missed <- dat %>%
  filter(Gold_Standard == "Included" & InRestrictedSearch == "No")

# Number of missed studies
N_missed <- nrow(missed)

# Total number of included studies
N_totalincluded <- nrow(dat %>% filter(Gold_Standard == "Included"))
```

# Calculate 'overinflated' performance of human TiAB if restricted search had been used 

```{r}
m_tiab_restricted_sen <- sensitivity(matched$Manual_TiAb, matched$Gold_Standard, positive = "Included")
m_tiab_restricted_spe <- specificity(dat$Manual_TiAb, dat$Gold_Standard, negative = "Excluded")
```

